Model

### 2019-08-25 stats/model.Rmd
add third model run

# load this for model parameters with wider prior on so_slope (0:3)
#sem_know_model <- readRDS("../saves/sem_know_new_model_2.rds")

# load this for model parameters with even wider prior on so_slope (0:4)
#sem_know_model <- readRDS("../saves/sem_know_new_model_3.rds")

@@

summary(novel_bm)

@@

```{r predictions pragmatic model ex 3 adults}
comb_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, combPred , sep='\n'),
  data =list(data = comb_model_data),
  data_var = "dataFromR"
)
# 
# #saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
# #inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
# 
comb_model_predictions <- comb_model_pred %>%
  separate(`0`, into = c("alignment","item", "age"), sep="/")%>%
  mutate(age = as.numeric(age))%>%
  rename( me_effect = `1`)%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         age = age + min(me_data$age_num),
         source = "Model")

 tail(comb_model_data)
```

@@

```{r}
ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source)) +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  geom_smooth(method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source), size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(condition~familiarObject)+
  facet_grid(alignment~item)+
  #ggtitle("Combination Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)
```

```{r}
#ggsave("../graphs/combination_model_data_by_item.pdf", width = 8, height = 2, scale = 1.5)
```

>>>>

# # load this for model parameters with wider prior on so_slope (0:3)
# sem_know_model <- readRDS("../saves/sem_know_new_model_2.rds")
# 
# # load this for model parameters with even wider prior on so_slope (0:4)
# sem_know_model <- readRDS("../saves/sem_know_new_model_3.rds")

@@

#summary(novel_bm)

@@

```{r predictions pragmatic model ex 3 adults}
comb_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, combPred , sep='\n'),
  data =list(data = comb_model_data),
  data_var = "dataFromR"
)

comb_model_predictions <- comb_model_pred %>%
  separate(`0`, into = c("alignment","item", "age"), sep="/")%>%
  mutate(age = as.numeric(age))%>%
  rename( me_effect = `1`)%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         age = age + min(me_data$age_num),
         source = "Model")

@@

```{r}
ggplot(data = data_comb, aes(x = age_num, y = correct, col = source, fill = source, lty = alignment)) +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_jitter(width = 0, height = 0.05, alpha = .6)+
  #geom_smooth(method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5)+
  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
  geom_line(data = comb_model_predictions, aes(x=age,y = me_effect, col = source, lty = alignment), size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(condition~familiarObject)+
  facet_grid(~item)+
  #ggtitle("Combination Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)
```

```{r}
ggsave("../graphs/combination_model_data_by_item.pdf", width = 8, height = 3, scale = 1.5)
```
